comgen-outline

### 2017-06-15 paper/comgen-paper.Rmd
elaborate discussion of books are paperbacks

(1) is often used to demonstrate that the property prevalence is not sufficient for a generic to be true.
The vast majority of books that exist are paperbacks; nonetheless *Books are paperbacks* sounds weird.
This is not an isolated example.
The same features can be observed in *Pastas are spaghetti*, *Animals are humans*.
These examples are generated by pairing a superordinate category with a property that describes a strictly subordinate category. 
We posit that the weirdness of these examples is the result of a failure of the comparison class.
If the comparison class can be derived with respect to the property [c.f., @Keil1979], one would expect the entities in the class to

>>>>

(1) is often used to demonstrate that the property prevalence is not sufficient for a generic to be true.
The vast majority of books that exist are paperbacks; nonetheless *Books are paperbacks* sounds weird.
This is not an isolated example.
The same features can be observed in *Pastas are spaghetti*, *Animals are humans*.
These examples are generated by pairing a superordinate category with a property that describes a strictly subordinate category. 
We posit that the weirdness of these examples is the result of a failure of the comparison class.
<!-- Specifically, the target category K in a generic statement "Ks F" is not expected to be in the comparison class.  -->

Though we have not introduced a theory of how a comparison class is contructed, relevant ideas may be found in @Keil1979.
His notion of *predicability* might relate to the comparison class, insofar as both may be derived with respect the property (e.g., the kinds of categories can be felicitiously predicated by "is paperback" may form a comparison class).
Note that this idea is similar to @Cohen1999's category of "Relative generics", which have truth conditions that are determined by a comparison to an alternative set of Ks (his Alt(K), our comparison class) which is composed of Ks that could satisfy some F in an an alternative set of Fs.
For example, being a paperback can only be true or false (in the predicability sense of @Keil1979) of individual books.
Aggregations of entities that can be predicated by the feature are, without further supporting context, categories of books.
Such categories may include books of different of different genres or eras, among plausibly many other such sub-categories.
From the taxonomic relation of the subordinate categories (e.g., types of books) to the target category (i.e., books), the true prevalence of the feature among the target category must be the mean of the prevalence of all subcategories, assuming an equal partitioning of the prior probability of subcategories.
Thus, if we were to construct a speaker model of the statement "Books are paperbacks", the model would predict a 0.5 endorsement: neither true nor untrue.
